An Analysis of Health & Lifestyle Factors Associated with Sleep Quality

### 2024-05-01 products/manuscript/Manuscript.qmd
Ref Troubleshoot

---
title: "An Analysis of Health & Lifestyle Factors Associated with Sleep Quality"
subtitle: ""
author: Kevin Kosewick and Emma Hardin-Parker
date: "4-29-2024"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: dataanalysis-references.bib
csl: apa.csl 
editor: 
  markdown: 
    wrap: 72
---

>>>>

---
title: "An Analysis of Health & Lifestyle Factors Associated with Sleep Quality"
subtitle: ""
author: Kevin Kosewick and Emma Hardin-Parker
date: "4-29-2024"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/sleepref2.bib
csl: ../../assets/apa.csl 
editor: 
  markdown: 
    wrap: 72
---
